---
title: "Customer Conversion Dashboard"
author: "Grace Sen"
format:
  dashboard:
    theme: cosmo
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(scales)

marketing <- read_csv("digital_marketing_campaign_dataset.csv")
```

# Overview

## Total Customers

```{r}
#| content: valuebox

nrow(marketing)
```

## Conversion Rate

```{r}
#| content: valuebox

scales::percent(mean(marketing$Conversion))
```

This dashboard summarizes customer demographics, campaign performance, customer engagement, email marketing, and purchase history to identify factors associated with customer conversion.

# Customer Demographics

## Age Distribution

```{r}
ggplot(marketing, aes(x = Age)) +
  geom_histogram(
    bins = 20,
    fill = "lightblue",
    color = "white"
  ) +
  labs(
    title = "Age Distribution",
    x = "Age",
    y = "Number of Customers"
  ) +
  theme_minimal()
```

## Income by Conversion

```{r}
ggplot(marketing,
       aes(x = factor(Conversion),
           y = Income)) +
  geom_boxplot(fill = "lightblue3") +
  labs(
    title = "Income by Conversion",
    x = "Conversion",
    y = "Income"
  ) +
  theme_minimal()
```

# Marketing Campaign

## Campaign Type

```{r}
ggplot(marketing,
       aes(x = CampaignType)) +
  geom_bar(fill = "lightblue") +
  labs(
    title = "Campaign Type Distribution",
    x = "Campaign Type",
    y = "Count"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 1))
```

## Conversion by Campaign

```{r}
ggplot(marketing,
       aes(x = CampaignType,
           fill = factor(Conversion))) +
  geom_bar(position = "fill") +
  scale_fill_manual(
    values = c(
      "0" = "lightblue",
      "1" = "lightsteelblue3"
    )
  ) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Conversion Rate by Campaign",
    x = "Campaign Type",
    y = "Proportion",
    fill = "Conversion"
  ) +
  theme_minimal()
```

# Customer Engagement

## Website Visits vs Time on Site

```{r}
ggplot(marketing,
       aes(x = WebsiteVisits,
           y = TimeOnSite,
           color = factor(Conversion))) +
  geom_point(alpha = 0.25,
             size = 1.2) +
  scale_color_manual(
    values = c(
      "0" = "lightblue",
      "1" = "steelblue3"
    )
  ) +
  labs(
    title = "Website Visits vs Time on Site",
    x = "Website Visits",
    y = "Time on Site",
    color = "Conversion"
  ) +
  theme_minimal()
```

## Website Visits by Conversion

```{r}
ggplot(marketing,
       aes(x = factor(Conversion),
           y = WebsiteVisits)) +
  geom_boxplot(fill = "lightblue") +
  labs(
    title = "Website Visits by Conversion",
    x = "Conversion",
    y = "Website Visits"
  ) +
  theme_minimal()
```

# Email Marketing

## Email Opens vs Clicks

```{r}
ggplot(marketing,
       aes(x = EmailOpens,
           y = EmailClicks,
           color = factor(Conversion))) +
  geom_point(alpha = 0.6) +
  scale_color_manual(
    values = c(
      "0" = "steelblue",
      "1" = "lightblue"
    )
  ) +
  labs(
    title = "Email Opens vs Email Clicks",
    x = "Email Opens",
    y = "Email Clicks",
    color = "Conversion"
  ) +
  theme_minimal()
```

# Purchase History

## Previous Purchases

```{r}
ggplot(marketing,
       aes(x = PreviousPurchases)) +
  geom_histogram(
    bins = 15,
    fill = "lightblue",
    color = "white"
  ) +
  labs(
    title = "Previous Purchases",
    x = "Previous Purchases",
    y = "Customers"
  ) +
  theme_minimal()
```

## Loyalty Points

```{r}
ggplot(marketing,
       aes(x = LoyaltyPoints,
           fill = factor(Conversion))) +
  geom_histogram(
    bins = 20,
    alpha = 0.8,
    position = "dodge",
    color = "white"
  ) +
  scale_fill_manual(
    values = c(
      "0" = "lightblue4",
      "1" = "lightblue"
    )
  ) +
  labs(
    title = "Loyalty Points",
    x = "Loyalty Points",
    fill = "Conversion"
  ) +
  theme_minimal()
```
